---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

This page is for Plotly.

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```


Here, I chose the instacart data.

```{r}
instacart = 
  instacart %>% 
  select(order_id, product_id, order_number, order_dow, order_hour_of_day, product_name, aisle, department) %>% 
  drop_na() 
```


## Make a line plot.
First, we can check the number of orders for different deparment during the day. 

```{r}
instacart %>%
  count(order_hour_of_day, department) %>%
  plot_ly(
    x = ~order_hour_of_day, y = ~n, type = "scatter", mode = "lines", color = ~department, colors = "viridis"
  )%>% 
  layout(title = "Number of Orders during the day")
```


## Plotly boxplot
Next, we can check the boxplot of the distributions of order_number during a week. Since the dataset instacart is too big, we peek inside by taking a sample with sample size 4000.

```{r}
instacart %>% 
  sample_n(4000) %>% 
  plot_ly(
    x = ~order_dow, y = ~order_number, type = "box", colors = "viridis"
  )%>% 
  layout(title = "Order number distribution during the week")
```


## Bar chart
At last, what aisles are popular? let's compare number of orders from different aisles by making a bar chart. Here, we only look at aisles with more that 20000 orders.

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarise(num_order = n()) %>% 
  filter(num_order > 20000) %>% 
  mutate(aisle = reorder(aisle, num_order)) %>% 
  plot_ly(
    x = ~aisle, y = ~num_order, type = "bar", colors = "viridis"
  ) %>% 
  layout(title = "Number of orders of different aisles")
```
